Distortion corrected kernel density estimate on Riemannian manifolds

### 2022-11-12 paper/paper.tex
Minor

Multivariate kernel density estimation (KDE see \textcite{Parzen1962-gt}; \textcite{Chen2017-dw} and references therein) is a fundamental tool for exploratory data analysis and unsupervised learning. Applications of KDE include finding hot spots of traffic networks in the GIS environment \autocite{Xie2008-eb,Okabe2009-nb}, automatic detection in visual surveillance systems \autocite{Elgammal2002-cw}, wind power density detection \autocite{Jeon2012-ac} and prime prediction via Twitter messages \autocite{Gerber2014-tq}. For \(m\)-dimensional data where \(m\) is even of moderate size, KDE is challenging due to the well-known curse of dimensionality. However, the manifold hypothesis suggests that many high-dimensional datasets belong to a \(d\)-dimensional manifold \(M\) where \(d\ll m\). The problem of KDE on manifolds has been well studied in @ \textcite{Hendriks1990-bt}, \textcite{Izenman1991-cj}, @\textcite{Pelletier2005-vu}, \textcite{Henry2013-da} and \textcite{Berenfeld2022-fd}. However, in these settings, it is assumed that the underlying manifold is known, which is rarely true in practice. Our objective in this paper is to propose KDE for data that lie on some unknown manifold.

>>>>

Multivariate kernel density estimation (KDE see \textcite{Parzen1962-gt}; \textcite{Chen2017-dw} and references therein) is a fundamental tool for exploratory data analysis and unsupervised learning. Applications of KDE include finding hot spots of traffic networks in the GIS environment \autocite{Xie2008-eb,Okabe2009-nb}, automatic detection in visual surveillance systems \autocite{Elgammal2002-cw}, wind power density detection \autocite{Jeon2012-ac} and prime prediction via Twitter messages \autocite{Gerber2014-tq}. For \(m\)-dimensional data where \(m\) is even of moderate size, KDE is challenging due to the well-known curse of dimensionality. However, the manifold hypothesis suggests that many high-dimensional datasets belong to a \(d\)-dimensional manifold \(M\) where \(d\ll m\). The problem of KDE on manifolds has been well studied in \textcite{Hendriks1990-bt}, \textcite{Izenman1991-cj}, \textcite{Pelletier2005-vu}, \textcite{Henry2013-da} and \textcite{Berenfeld2022-fd}. However, in these settings, it is assumed that the underlying manifold is known, which is rarely true in practice. Our objective in this paper is to propose KDE for data that lie on some unknown manifold.
